text graveyard

### 2023-05-19 scripts/manuscript/graveyard.qmd
Committing before making a big change to code

>>>>

         ` ` = as.factor(` `) %>% fct_relevel('Overall',
                           'Age: 18 to 44',
                           'Age: 45 to 64',
                           'Age: 65 to 74',
                           'Age: 75+',
                           'Sex: Female',
                           'Sex: Male',
                           'Race/Ethnicity: Asian/Not Hispanic',
                           'Race/Ethnicity: Black/Not Hispanic',
                           'Race/Ethnicity: Hispanic',
                           'Race/Ethnicity: White/Not Hispanic',
                           'Highest degree earned: Greater than high school',
                           'Highest degree earned: High school',
                           'Highest degree earned: Less than high school',
                           'Insurance coverage: Medicaid',
                           'Insurance coverage: Medicare only',
                           'Insurance coverage: Private only',
                           'Insurance coverage: Uninsured',
                           'Poverty income ratio: > 400%',
                           'Poverty income ratio: 200% - 399%',
                           'Poverty income ratio: 100% - 199%',
                           'Poverty income ratio: < 100%')) %>%

# This code here changes the apc values to NA if they aren't significant, but I think
    # what I need to do is change the APC values if there are no identified joinpoints
    # across(
    #   c(apc_0, apc_95_lcl_0, apc_95_ucl_0),
    #   ~ case_when(p_value_0 > 0.05 &
    #                 p_value_1 > 0.05 & p_value_2 > 0.05 & p_value_3 > 0.05 ~ NA_real_,
    #               TRUE ~ .x)
    # ),
    # across(
    #   c(apc_1, apc_95_lcl_1, apc_95_ucl_1),
    #   ~ case_when(p_value_0 > 0.05 &
    #                 p_value_1 > 0.05 & p_value_2 > 0.05 & p_value_3 > 0.05 ~ NA_real_,
    #               TRUE ~ .x)
    # ),
    # across(
    #   c(apc_2, apc_95_lcl_2, apc_95_ucl_2),
    #   ~ case_when(p_value_0 > 0.05 &
    #                 p_value_1 > 0.05 & p_value_2 > 0.05 & p_value_3 > 0.05 ~ NA_real_,
    #               TRUE ~ .x)
    # ),
    # across(
    #   c(apc_3, apc_95_lcl_3, apc_95_ucl_3),
    #   ~ case_when(p_value_0 > 0.05 &
    #                 p_value_1 > 0.05 & p_value_2 > 0.05 & p_value_3 > 0.05 ~ NA_real_,
    #               TRUE ~ .x)
    # ),

```{r all-plots}

stats_table_plot_dat <- jp_proportion_plot_data %>%
  mutate(model = as.numeric(model)) %>% 
  filter(strata != 'Total') %>%
  filter(strata != 'Not available') %>% 
  filter(strata != 'Other Race/Not Hispanic') %>% 
  filter(strata != 'Other') %>% 
  mutate(variable_text = case_when(variable == 'a1c' ~ 'Two or more A1C tests',
                                   variable == 'CHOL_all' ~ 'Cholesterol tested',
                                   variable == 'DENT_all' ~ 'One or more dentist visits',
                                   variable == 'eye-exam' ~ 'Eye exam with dilation',
                                   variable == 'flu' ~ 'Received flu vaccine',
                                   variable == 'foot' ~ 'Foot examination'),
         strata = case_when(strata == 'stat_0' ~ 'Overall',
                            TRUE ~ strata)) %>% 
  mutate(strata = as.factor(strata)) %>% 
  split(., f = .$stratifier)

stats_table_plot_dat <- map(stats_table_plot_dat, function(.x) {
  .x %>% 
    mutate(strata = fct_drop(strata))
})

overall_data <- stats_table_plot_dat$overall %>% 
  mutate(strata = case_when(strata == 'Overall' ~ 'z'))
# Remove the overall data from the list
stats_table_plot_dat <- stats_table_plot_dat[-4]
# Relevel the poverty factors
stats_table_plot_dat$poverty$strata <-
  factor(
    stats_table_plot_dat$poverty$strata,
    levels = c('High income', 'Middle income', 'Low income', 'Poor/Negative'),
    labels = c(
      '> 400% ',
      '200% - 399%',
      '100% - 199%',
      '< 100%'

    )
  )
test_plots <- stats_table_plot_dat %>% 
   map(
    ~ ggplot(filter(.x, variable %in% c('a1c', 'CHOL_all', 'flu')),
             aes(
      x = year,
      y = p,
      group = strata,
      color = strata
    )) +
      #geom_point() +
      geom_line(aes(x = year, y = model, group = strata, color = strata)) +
      geom_line(data = filter(overall_data, variable %in% c('a1c', 'CHOL_all', 'flu')),
                  aes(x = year, y = model),
                  color = 'black',
                  linetype = 'dashed') +
      facet_wrap( ~ variable_text, ncol = 3) +
      theme_classic() +
      scale_y_continuous(
        limits = c(00, 100),
        breaks = seq(0, 100, 25),
        labels = seq(0, 100, 25)
      ) +
      scale_x_continuous(
        limits = c(2008, 2020),
        breaks = seq(2008, 2020, 2),
        labels = seq(2008, 2020, 2)
      ) +
      scale_color_brewer(type = 'qual', palette = 'Set2') +
      theme(axis.text = element_text(color = 'black'),
            axis.text.x = element_text(angle = 45, hjust = 0.9, vjust = 0.95),
            legend.title = element_text(size = 8),
            legend.text = element_text(size = 6)) +
      labs(x = 'Year', y = 'Percentage')
  )

test_plots[[1]] <- test_plots[[1]] + labs(color = 'Age (grouped)') +
  theme(axis.title.x = element_blank())
test_plots[[2]] <-
  test_plots[[2]] + labs(color = 'Highest degree \nobtained') + theme(
    strip.background =  element_blank(),
    strip.text = element_blank(),
    axis.title.x = element_blank()
  )
test_plots[[3]] <-
  test_plots[[3]] + labs(color = "Insurance") + theme(
    strip.background =  element_blank(),
    strip.text = element_blank(),
    axis.title.x = element_blank()
  )
test_plots[[4]] <-
  test_plots[[4]] + labs(color = 'Poverty income ratio') + theme(
    strip.background =  element_blank(),
    strip.text = element_blank()
  )
test_plots[[5]] <-
  test_plots[[5]] + labs(color = 'Race & Ethnicity') + theme(
    strip.background =  element_blank(),
    strip.text = element_blank(),
    axis.title.x = element_blank()
  )
test_plots[[6]] <-
  test_plots[[6]] + labs(color = 'Sex') + theme(strip.background =  element_blank(),
                                                strip.text = element_blank(),
    axis.title.x = element_blank())
test_plots <- list(
  test_plots[[1]],
  test_plots[[6]],
  test_plots[[5]],
  test_plots[[2]],
  test_plots[[3]],
  test_plots[[4]]
)

exam_plots <- stats_table_plot_dat %>% 
   map(
    ~ ggplot(filter(.x, variable %!in% c('a1c', 'CHOL_all', 'flu')),
             aes(
      x = year,
      y = p,
      group = strata,
      color = strata
    )) +
      #geom_point() +
      geom_line(aes(x = year, y = model, group = strata, color = strata)) +
      geom_line(data = filter(overall_data, variable %!in% c('a1c', 'CHOL_all', 'flu')),
                  aes(x = year, y = model),
                  color = 'black',
                  linetype = 'dashed') +
      facet_wrap( ~ variable_text, ncol = 3) +
      theme_classic() +
      scale_y_continuous(
        limits = c(  0, 100),
        breaks = seq(0, 100, 25),
        labels = seq(0, 100, 25)
      ) +
      scale_x_continuous(
        limits = c(2008, 2020),
        breaks = seq(2008, 2020, 2),
        labels = seq(2008, 2020, 2)
      ) +
      scale_color_brewer(type = 'qual', palette = 'Set2') +
      theme(axis.text = element_text(color = 'black'),
            axis.text.x = element_text(angle = 45, hjust = 0.9, vjust = 0.95),
            legend.title = element_text(size = 8),
            legend.text = element_text(size = 7)) +
      labs(x = 'Year', y = 'Percentage')
  )

exam_plots[[1]] <- exam_plots[[1]] + labs(color = 'Age (grouped)') +
  theme(axis.title.x = element_blank())
exam_plots[[2]] <-
  exam_plots[[2]] + labs(color = 'Highest degree \nobtained') + theme(
    strip.background =  element_blank(),
    strip.text = element_blank(),
    axis.title.x = element_blank()
  )
exam_plots[[3]] <-
  exam_plots[[3]] + labs(color = "Insurance") + theme(
    strip.background =  element_blank(),
    strip.text = element_blank(),
    axis.title.x = element_blank()
  )
exam_plots[[4]] <-
  exam_plots[[4]] + labs(color = 'Poverty income ratio') + theme(
    strip.background =  element_blank(),
    strip.text = element_blank()
  )
exam_plots[[5]] <-
  exam_plots[[5]] + labs(color = 'Race & Ethnicity') + theme(
    strip.background =  element_blank(),
    strip.text = element_blank(),
    axis.title.x = element_blank()
  )
exam_plots[[6]] <-
  exam_plots[[6]] + labs(color = 'Sex') + theme(strip.background =  element_blank(),
                                                strip.text = element_blank(),
    axis.title.x = element_blank())
exam_plots <- list(
  exam_plots[[1]],
  exam_plots[[6]],
  exam_plots[[5]],
  exam_plots[[2]],
  exam_plots[[3]],
  exam_plots[[4]]
)

# all_exam_plots <- exam_plots %>% 
#   wrap_plots(nrow = 6) &
#   theme(plot.margin = margin(0.5, 0.5, 0.5, 0.5, 'pt'))
# all_test_plots <- test_plots %>% 
#   wrap_plots(nrow = 6) &
#   theme(plot.margin = margin(0.5, 0.5, 0.5, 0.5, 'pt'))
```

Youngest age group was consistently lower than all others for cholesterol testing and receiving flu vaccine, and eye exam and foot exam

Hispanic - lowest, although close for cholesterol and A1C (A1C until \~ 2018). And eye exam, but again real close

\< HS consistently lower on all exams and A1c tests Uninsured lower on everything

Flu - lots of increases. Hung et al found no change over 2007 - 2018 using NHIS data

Cholesterol - a few decreases

A1C - a few increases

Dentists - kind of all over the place; Aldosari 2022 found no difference in utilization between people with diabetes and without (so not a trend analysis). Luo et al 2018 found declines for people with diabetes from 2004 - 2014

Foot exams - mostly all flat, except older. PEraj 2019 found that Hispanic americans and asian-americans were significantly less likely to have a foot exam

Eye exams - mostly flat or decreasing, except uninsured. Chen 2020 found there were increases after Medicaid expansion but only for the first two years. Eppley 2019 found no change in adherance from 2005 to 2016 using NHANES

Mostly flat, some decreases.
